Simulations log

### 2020-04-04 manuscript/drafts/manuscript.Rmd
update datasets in manuscript

---
title: "Manuscript drafts"
author: "Gerbrich Ferdinands"
date: "1/14/2020"
output:
   pdf_document:
  #   citation_package: biblatex
bibliography: asreview.bib
---

@@

#pathRdata <- "../../R/data/"
pathRdata <- "data/"

```

@@

```{r}
# datasets table
load(paste0(pathRdata, "datasets_table.Rdata"))

@@

## Simulations
To evaluate performance of the five models described above, the model is used to simulate five existing systematic reviews.

@@

A simulation is of one model on one dataset. 
The simulation is repeated for 10 trials $t$.

Every simulation study consists of 10 trials, to account for the randomness of prior inclusions and exclusions.
So every trial the prior inclusions and exclusions are randomly selected. 
Results are aggregated (?)

>>>>

---
title: "Manuscript drafts"
author: "Gerbrich Ferdinands"
date: "1/14/2020"
output:
   pdf_document:
     citation_package: biblatex
bibliography: asreview.bib
---

@@

#pathRdata <- "data/"
pathRdata <- "../../datasets/data_statistics/"
```

@@

```{r}
# datasets table
drops <- readRDS(paste0(pathRdata, "drops.RDS"))
all <- readRDS(paste0(pathRdata, "all.RDS"))

@@

## Simulations
To evaluate performance of the five models described above, the model is used to simulate five existing systematic reviews. 
A simulation is of one model on one dataset. 
The simulation is repeated for 15 trials $t$.

The starting point of the active learning model in the simulation is one prior included publication and one prior excluded publication. 
The training set is randomly sampled from the data. 
Every simulation study consists of 15 trials, to account for the randomness of prior inclusions and exclusions.
So every trial the prior inclusions and exclusions are randomly selected. 
Results are aggregated (?)

@@

### 2020-04-04 simulation_study/hpoptimization/README.Rmd
add config file LCTD all
update datasets in manuscript

---
title: "log hyperparameter optimization"
output: html_notebook
---

@@

>>>>

---
title: "Hyperparameter optimization log"
output: github_document
---

@@

```{r}
# all - BCTD gets a few extra
hpsets["BCTD",, "all"] <- 1 # 7893274 (12 hours)
# all - LCTD is done
```

04.04.2020
```{r}
# rf all is done 
hpsets["RCTD",,"all"] <- 2 
hpsets["BCTD",, "all"] <- 2 
```

### 2020-04-04 simulation_study/simulation/README.Rmd
update datasets in manuscript

---
title: "README"
output: github_document
---

@@

# transfer to harddrive 
transfer("hp", condition[8])
#sims[condition[8], , "one"] <- 3 # output is on harddrive
```

all - LCTD hyperparameters 
```{r}
# manually transform
# push to github 
sims[condition[4], , "all"] <- 1 # configs are on github 
```

>>>>

---
title: "Simulations log"
output: github_document
---

@@

# transfer to harddrive 
transfer("one", condition[8])
#sims[condition[8], , "one"] <- 3 # output is on harddrive
```

all - LCTD hyperparameters 
```{r}
# manually transform
# push to github 
sims[condition[4], , "all"] <- 1 # configs are on github

# run simulations 
lctd_n <- createLines(condition[4], d, "all")
write.table(lctd_n, file = "scripts/n/lctd_n.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
names(lctd_n) <- c()
#sims[condition[4], d, "all"] <- 2 # simulations are running

# transfer to harddrive 
transfer("n", condition[4])
#sims[condition[8], , "one"] <- 3 # output is on harddrive
```
